---
title: "Credit Cards Default"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)

### Data exploration
library(janitor)
library(skimr)
library(DataExplorer)
library(plotly)
library(vip)

### ML
library(tidymodels)
library(h2o)

### SMOTE
library(DMwR)

### Data wrangling
library(tidyverse)

load('../../03_env/eda_data.RData')
load('../../03_env/total_metrics.RData')
load('../../03_env/log_data.RData')
load('../../03_env/gains_n_lift.RData')
load('../../03_env/data_problems.RData')
```

Feature description {data-orientation=rows}
====================================

Row { vertical_layout: scroll, data-height=1700 }
-----------------------------------------------------------------------

### Predefined dataset variables - cleaned

```{r}
knitr::kable(variables_tbl)
```

Row { vertical_layout: scroll, data-height=1700 }
-----------------------------------------------------------------------

### Custom engineered variables

```{r}
knitr::kable(variables_custom_tbl)
```

Exploratory Data Analysis {data-orientation=rows}
====================================

Row {data-height=750}
-----------------------------------------------------------------------

### Correlation plot
```{r}
corr_funnel_plot
```

Row
-----------------------------------------------------------------------

### Class balance

```{r}
plot_class_balance
```


### Default per gender

```{r}
plot_sex
```

Row
-----------------------------------------------------------------------

### Age grouped

```{r}
plot_age
```


### Education
```{r}
plot_education
```

### Marriage 
```{r}
plot_marriage
```

Row
------------------------------

### Months not paid
```{r}
plot_months_not_paid
```

### Months not paid
```{r}
plot_months_not_paid_sum
```

### Months not paid
```{r}
plot_months_not_paid_sum_cat
```

Row { .tabset .tabset-fade }
----------------------------------------------------------------------

### Pay_1 

```{r}
plot_pay_1 %>% layout(width = 900)
```

### Pay_2 

```{r}
plot_pay_2 %>% layout(width = 900)
```

### Pay_3 

```{r}
plot_pay_3 %>% layout(width = 900)
```

### Pay_4

```{r}
plot_pay_4 %>% layout(width = 900)
```

### Pay_5

```{r}
plot_pay_5 %>% layout(width = 900)
```

### Pay_6

```{r}
plot_pay_6 %>% layout(width = 900)
```

Model comparison {data-orientation=rows}
=======================================================

Row { vertical_layout: fill }
-----------------------------------------------------------------------

### Metrics

```{r}
knitr::kable(metrics_tbl)
```


Row { vertical_layout: fill }
-----------------------------------------------------------------------
### All Models

```{r}
DT::datatable(total_metrics)
```
<style> #DTtest{ overflow: auto; } </style>


Final Comparison {data-orientation=rows}
============================

Row
---------------------

### Model comparison

```{r}
DT::datatable(data = comparison_tbl)
```

Row
-------------------

### LightGBM - Threshold

```{r}
lgbm_comp_rate_mat_plot
```

### Logistic Regression - Tuned + SMOTE

```{r}
glm_smote_comp_rate_mat_plot
```

### Logistic Regression - Not tuned

```{r}
log_comp_rate_mat_plot
```


Business Science { data-orientation=rows }
=======================

Row 
------------------

### Gains and Lifts table

```{r}
DT::datatable(gains_lift)
```

Row
------

```{r}
knitr::kable(desc_tbl %>% rename(Vrednost = name, Opis = desc))
```

Row
------------------

### ROC Curve

```{r}
roc_plot %>% plotly::layout(legend = list(orientation = "h", x = 0, y = -0.3))
```


### Precision vs Recall

```{r}
pr_plot %>% plotly::layout(legend = list(orientation = "h", x = 0, y = -0.3))
```



Row
------------------

### Gains chart

```{r}
gains_plot %>% plotly::layout(legend = list(orientation = "h", x = 0, y = -0.3))
```


### Lift chart

```{r}
lift_plot %>% plotly::layout(legend = list(orientation = "h", x = 0, y = -0.3))
```

<!-- Row -->
<!-- ----- -->

<!-- ### Expected Profit Curve -->

<!-- ```{r} -->
<!-- threshold_profit_plot %>% plotly::layout(legend = list(orientation = 'h', x = 0, y = -0.3)) -->
<!-- ``` -->


Row
-----

### Cost and Benefits table

```{r}
knitr::kable(cb_tbl %>% rename(Rate = type, Cost = cost, Benefit = benefit))
```


Data problems {data-orientation=rows}
=====================================

Row
-----

### Description

```{r}
knitr::kable(data_problems_tbl)
```

Row
-------

### Bill amount < 0

```{r}
DT::datatable(bill_amt_ltz %>% select(default, contains('bill')))
```

Row
-------

### Duly paid yet default

```{r}
DT::datatable(duly_paid_default %>% select(default, contains('pay'), -contains('rate'), contains('bill')))
```

Row
-------

### Remaining amount < 0

```{r}
DT::datatable(rem_ltz %>% select(-rowname))
```

