---
title: "Credit Cards Default"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)

### Data exploration
library(janitor)
library(skimr)
library(DataExplorer)
library(plotly)
library(vip)

### ML
library(tidymodels)
library(h2o)

### SMOTE
library(DMwR)

### Data wrangling
library(tidyverse)

load('../../03_env/eda_data.RData')
load('../../03_env/total_metrics.RData')
load('../../03_env/log_data.RData')
load('../../03_env/gains_n_lift.RData')
load('../../03_env/data_problems.RData')
```

Feature description {data-orientation=rows}
====================================

Row { vertical_layout: scroll, data-height=1700 }
-----------------------------------------------------------------------

### Predefined dataset variables - cleaned

```{r}
knitr::kable(variables_tbl)
```

Row { vertical_layout: scroll, data-height=1700 }
-----------------------------------------------------------------------

### Custom engineered variables

```{r}
knitr::kable(variables_custom_tbl)
```

Exploratory Data Analysis {data-orientation=rows}
====================================

Row {data-height=750}
-----------------------------------------------------------------------

### Correlation plot
```{r}
corr_funnel_plot
```

Row
-----------------------------------------------------------------------

### Class balance

```{r}
plot_class_balance
```


### Default per gender

```{r}
plot_sex
```

Row
-----------------------------------------------------------------------

### Age grouped

```{r}
plot_age
```


### Education
```{r}
plot_education
```

### Marriage 
```{r}
plot_marriage
```

Row
------------------------------

### Months not paid
```{r}
plot_months_not_paid
```

### Months not paid
```{r}
plot_months_not_paid_sum
```

### Months not paid
```{r}
plot_months_not_paid_sum_cat
```

Row { .tabset .tabset-fade }
----------------------------------------------------------------------

### Pay_1 

```{r}
plot_pay_1 %>% layout(width = 900)
```

### Pay_2 

```{r}
plot_pay_2 %>% layout(width = 900)
```

### Pay_3 

```{r}
plot_pay_3 %>% layout(width = 900)
```

### Pay_4

```{r}
plot_pay_4 %>% layout(width = 900)
```

### Pay_5

```{r}
plot_pay_5 %>% layout(width = 900)
```

### Pay_6

```{r}
plot_pay_6 %>% layout(width = 900)
```

Model comparison {data-orientation=rows}
=======================================================

Row { vertical_layout: fill }
-----------------------------------------------------------------------

### Metrics

```{r}
knitr::kable(metrics_tbl)
```


Row { vertical_layout: fill }
-----------------------------------------------------------------------
### All Models

```{r}
DT::datatable(total_metrics)
```
<style> #DTtest{ overflow: auto; } </style>



XGBoost {data-orientation=rows}
=======================================================================

Row
-----------------------------------------------------------------------

### Xgboost scores

```{r}
DT::datatable(xgb_metrics)
```


Row
-----------------------------------------------------------------------

### Xgboost - Confusion matrix

```{r}
conf_xgb_reg +
  theme(legend.position = 'None')
```   

### Xgboost - Confusion matrix

```{r}
conf_xgb_reg_ts +
  theme(legend.position = 'None')
```   

### Xgboost - Variable importance plot

```{r}
vip_xgb +
  theme(axis.text = element_text(size = 13))
```

Row
-----------------------------------------------------------------------

### Xgboost Downsampling - Confusion Matrix

```{r}
conf_xgb_down +
  theme(legend.position = 'None')
```

### Xgboost Downsampling - Confusion Matrix - Optimal Threshold

```{r}
conf_xgb_down_ts +
  theme(legend.position = 'None')
```

### Xgboost Downsampling - Variable importance plot

```{r}
vip_xgb_down +
  theme(axis.text = element_text(size = 13))
```

Row
-----------------------------------------------------------------------

### Xgboost Upsampling - Confusion Matrix

```{r}
conf_xgb_up +
  theme(legend.position = 'None')
```

### Xgboost Upsampling - Confusion Matrix - Optimal Threshold

```{r}
conf_xgb_up_ts +
  theme(legend.position = 'None')
```

### Xgboost Upsampling - Variable Importance Plot

```{r}
vip_xgb_up +
  theme(axis.text = element_text(size = 13))
```


Row
-----------------------------------------------------------------------

### Xgboost SMOTE - Confusion Matrix

```{r}
conf_xgb_smote +
  theme(legend.position = 'None')
```

### Xgboost SMOTE - Confusion Matrix - Optimal Threshold

```{r}
conf_xgb_smote_ts +
  theme(legend.position = 'None')
```

### Xgboost SMOTE - Variable Importance Plot

```{r}
vip_xgb_smote +
  theme(axis.text = element_text(size = 13))
```


LightGBM {data-orientation=rows}
=======================================================================

Row
-----------------------------------------------------------------------

### LightGBM scores

```{r}
DT::datatable(lgbm_metrics)
```


Row
-----------------------------------------------------------------------

### LightGBM - Confusion matrix

```{r}
conf_lgbm_reg +
  theme(legend.position = 'None')
```   

### LightGBM - Confusion matrix - Optimal Threshold

```{r}
conf_lgbm_reg_ts +
  theme(legend.position = 'None')
```   

### Variable Importance Plot

```{r}
vip_lgbm_reg +
  theme(axis.text = element_text(size = 13))
```


Row
-----------------------------------------------------------------------

### LightGBM Downsampling - Confusion Matrix

```{r}
conf_lgbm_down +
  theme(legend.position = 'None')
```

### LightGBM Downsampling - Confusion Matrix - Optimal Threshold

```{r}
conf_lgbm_down_ts +
  theme(legend.position = 'None')
```

### Variable Importance Plot

```{r}
vip_lgbm_down +
  theme(axis.text = element_text(size = 13))
```


Row
-----------------------------------------------------------------------

### LightGBM Upsampling - Confusion Matrix

```{r}
conf_lgbm_up +
  theme(legend.position = 'None')
```

### LightGBM Upsampling - Confusion Matrix - Optimal Threshold

```{r}
conf_lgbm_up_ts +
  theme(legend.position = 'None')
```

### Variable Importance Plot

```{r}
vip_lgbm_up +
  theme(axis.text = element_text(size = 13))
```



Row
-----------------------------------------------------------------------

### LightGBM SMOTE - Confusion Matrix

```{r}
conf_lgbm_smote +
  theme(legend.position = 'None')
```

### LightGBM SMOTE - Confusion Matrix

```{r}
conf_lgbm_smote_ts +
  theme(legend.position = 'None')
```

### Variable Importance Plot

```{r}
vip_lgbm_smote +
  theme(axis.text = element_text(size = 13))
```


Logistic Regression {data-orientation=rows}
====================================

Row
-------------------------------------------------

```{r}
DT::datatable(glm_metrics %>% filter(str_starts(model, 'GLMNET ')))
```


Row
-------------------------------------------------------------

### Logistic Regression - Confusion Matrix

```{r}
conf_glm_regular
```

### Logistic Regression - Confusion Matrix - Optimal Threshold

```{r}
conf_glm_regular_ts
```

### Logistic Regression - Variable Importance Plot

```{r}
vip_glm_reg +
  theme(axis.text = element_text(size = 13))
```   

Row
-------------------------------------------------------------

### Logistic Regression Downsample - Confusion Matrix

```{r}
conf_glm_down
```

### Logistic Regression Downsample - Confusion Matrix - Optimal Threshold

```{r}
conf_glm_down_ts
```

### Logistic Regression Downsample - Variable Importance Plot

```{r}
vip_glm_down +
  theme(axis.text = element_text(size = 13))
```   

Row
-------------------------------------------------------------

### Logistic Regression Upsample - Confusion Matrix

```{r}
conf_glm_up
```

### Logistic Regression Upsample - Confusion Matrix - Optimal Threshold

```{r}
conf_glm_up_ts
```

### Logistic Regression Upsample - Variable Importance Plot

```{r}
vip_glm_up +
  theme(axis.text = element_text(size = 13))
```   


Row
-------------------------------------------------------------

### Logistic Regression SMOTE - Confusion Matrix

```{r}
conf_glm_smote
```

### Logistic Regression SMOTE - Confusion Matrix - Optimal Threshold

```{r}
conf_glm_smote_ts
```

### Logistic Regression SMOTE - Variable Importance Plot

```{r}
vip_glm_smote +
  theme(axis.text = element_text(size = 13))
```   





Logistic Regression - X3, X7, X9 {data-orientation=rows}
====================================

Row
-------------------------------------------------

```{r}
DT::datatable(glm_metrics %>% filter(str_starts(model, 'GLMNET3')))
```


Row
-------------------------------------------------------------

### Logistic Regression - X3, X7, X9 - Confusion Matrix

```{r}
conf_glm3_regular
```

### Logistic Regression - X3, X7, X9 - Confusion Matrix - Optimal Threshold

```{r}
conf_glm3_regular_ts
```

### Logistic Regression - X3, X7, X9 - Variable Importance Plot

```{r}
vip_glm3_reg +
  theme(axis.text = element_text(size = 13))
```   

Row
-------------------------------------------------------------

### Logistic Regression Downsample - X3, X7, X9 - Confusion Matrix

```{r}
conf_glm3_down
```

### Logistic Regression Downsample - X3, X7, X9 - Confusion Matrix - Optimal Threshold

```{r}
conf_glm3_down_ts
```

### Logistic Regression Downsample - X3, X7, X9 - Variable Importance Plot

```{r}
vip_glm3_down +
  theme(axis.text = element_text(size = 13))
```   

Row
-------------------------------------------------------------

### Logistic Regression Upsample - X3, X7, X9 - Confusion Matrix

```{r}
conf_glm3_up
```

### Logistic Regression Upsample - X3, X7, X9 - Confusion Matrix - Optimal Threshold

```{r}
conf_glm3_up_ts
```

### Logistic Regression Upsample - X3, X7, X9 - Variable Importance Plot

```{r}
vip_glm3_up +
  theme(axis.text = element_text(size = 13))
```   


Row
-------------------------------------------------------------

### Logistic Regression SMOTE - X3, X7, X9 - Confusion Matrix

```{r}
conf_glm3_smote
```

### Logistic Regression SMOTE - X3, X7, X9 - Confusion Matrix - Optimal Threshold

```{r}
conf_glm3_smote_ts
```

### Logistic Regression SMOTE - X3, X7, X9 - Variable Importance Plot

```{r}
vip_glm3_smote +
  theme(axis.text = element_text(size = 13))
```   


Final Comparison {data-orientation=rows}
============================

Row
---------------------

### Model comparison

```{r}
# temp <- bind_rows(total_metrics %>% filter(model %in% c('Lightgbm - Threshold', 'GLMNET SMOTE')),
#           log_metrics) %>% 
#   select(-library)

DT::datatable(data = comparison_tbl)
```



<!-- Row -->
<!-- ------------------- -->

<!-- ### LightGBM - Threshold -->

<!-- ```{r} -->
<!-- lgbm_comp_conf_mat_plot -->
<!-- ``` -->

<!-- ### Logistic Regression - Tuned + SMOTE -->

<!-- ```{r} -->
<!-- glm_smote_comp_conf_mat_plot -->
<!-- ``` -->

<!-- ### Logistic Regression - Not tuned -->

<!-- ```{r} -->
<!-- log_comp_conf_mat_plot -->
<!-- ``` -->


Row
-------------------

### LightGBM - Threshold

```{r}
lgbm_comp_rate_mat_plot
```

### Logistic Regression - Tuned + SMOTE

```{r}
glm_smote_comp_rate_mat_plot
```

### Logistic Regression - Not tuned

```{r}
log_comp_rate_mat_plot
```



Business Science { data-orientation=rows }
=======================

Row 
------------------

### Gains and Lifts table

```{r}
DT::datatable(gains_lift)
```

Row
------

```{r}
knitr::kable(desc_tbl %>% rename(Vrednost = name, Opis = desc))
```

Row
------------------

### ROC Curve

```{r}
roc_plot %>% plotly::layout(legend = list(orientation = "h", x = 0, y = -0.3))
```


### Precision vs Recall

```{r}
pr_plot %>% plotly::layout(legend = list(orientation = "h", x = 0, y = -0.3))
```



Row
------------------

### Gains chart

```{r}
gains_plot %>% plotly::layout(legend = list(orientation = "h", x = 0, y = -0.3))
```


### Lift chart

```{r}
lift_plot %>% plotly::layout(legend = list(orientation = "h", x = 0, y = -0.3))
```

Row
-----

### Expected Profit Curve

```{r}
threshold_profit_plot %>% plotly::layout(legend = list(orientation = 'h', x = 0, y = -0.3))
```


Row
-----

### Cost and Benefits table

```{r}
knitr::kable(cb_tbl %>% rename(Rate = type, Cost = cost, Benefit = benefit))
```


Data problems {data-orientation=rows}
=====================================

Row
-----

### Description

```{r}
knitr::kable(data_problems_tbl)
```

Row
-------

### Bill amount < 0

```{r}
DT::datatable(bill_amt_ltz %>% select(default, contains('bill')))
```

Row
-------

### Duly paid yet default

```{r}
DT::datatable(duly_paid_default %>% select(default, contains('pay'), -contains('rate'), contains('bill')))
```

Row
-------

### Remaining amount < 0

```{r}
DT::datatable(rem_ltz %>% select(-rowname))
```


<!-- Row -->
<!-- ------------------------------------------------------------- -->


<!-- ### Stacked Ensemble All -->

<!-- ```{r} -->
<!-- # stacked_all_conf_mat -->
<!-- ``` -->

<!-- ### Stacked Ensemble Top 5 -->

<!-- ```{r} -->
<!-- # stacked_top_5_conf_mat -->
<!-- ``` -->


